\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage[letterpaper, left=1.0in, right=1.0in, top=1.0in, bottom=1.0in]{geometry}

\signature{Andrew~J.~Steinmetz~\&~Johann~Rafelski}
\address{The University of Arizona\\Tucson, AZ 85737, USA}
\date{March 24, 2025}

\begin{document}

\begin{letter}{Managing Editors\\European Physical Journal Special Topics\\Special Issue ``Particles and Plasmas''}
\opening{Dear Editors,}
 
Please find our improved contribution to the EPJ Special Issue ``Particles and Plasmas,'' prepared in order to respond to the kind suggestions made by our referees, for which we are grateful. Our changes (see attached document below) are marked in blue, and any trivial grammatical changes or corrections remain unmarked. This is a summary of relevant changes made:

\begin{enumerate}
    \item The abstract and conclusions have seen many small changes and improvements, these are marked in blue entirely.
    \item As requested by Reviewer \#2, Section~1 (\textit{Introduction}) has been given an intro paragraph  to clarify context and avoid ``in medias res''.  
    \item Figure~1 has been updated to align with comments in text.
    \item The captions of both Table~1 and Figure~1 have been revised as requested by Reviewers \#1 and \#2.
    \item The introduction has been broken into two sections: Section~1 and Section~2 (\textit{Estimation of plasma spin magnetization}). This better connects to the ending of the article as requested by Reviewers \#1 and \#2.
    \item List of minor changes requested by Reviewer \#2:
    \begin{enumerate}
        \item All mentions of pico- or nano-scale have been explicitly defined.
        \item Natural units have been more carefully introduced.
        \item The appearance of the index ``i'' has been fixed.
        \item ``CPT'' has been changed to ``CPT symmetry''.
        \item We updated the notation for ``s'' and ``$\sigma$''.
        \item Citations for the hadronization temperature have been included.
        \item The acknowledgment credit have been revised.
    \end{enumerate}
    \item As requested by Reviewers \#1 and \#2, the mathematical framework presented in Section~4 (\textit{Magnetized grand partition function}) has been updated. Subsections were retitled as a result. 
    \item As requested by Reviewer \#2, 11 new references have been added to provide more background information and reference key statements.
\end{enumerate}

We look forward to moving to the next step in the publication process.

\closing{Yours Sincerely,}

\end{letter}

\end{document}

